Coherent Hyper-Raman Four Wave Mixing Vibrational Spectroscopies

### 2024-06-14 paper.tex
Update paper.tex

\graphicspath{{"figures/"}}
\begin{document}
%Title of paper
\title{Coherent Hyper-Raman Four Wave Mixing Spectroscopies}

@@

Most quantitative methods in an n$^{th}$ order CMDS experiment are used to extract $\chi^{(n)}$ values for comparing the relative strength of nonlinear processes in different media. \cite{Zhu87, RN351, RN345}
The recorded $\chi^{(n)}$ values provide insight into how microscopic quantities ($\vec{\mu}, \alpha_{ij}, \beta_{ijk}$) impact nonlinear output.
To our knowledge, only vibraitonal SFG and 2D-IR spectroscopy has taken advantage of orientationally averaged $\chi^{(n)}$ values to extract transition moments. \cite{Shen90, Moilanen2009, RN245}
Previous treatments did not consider using quantitative analysis in SIVE to measure $\beta_{ijk}$ values from SIVE spectra.
It is thus useful to investigate how a simple treatment of orientational averaging can extract $\beta_{ijk}$ from a $\chi^{(3)}_{IJKL}$ expression.

The SIVE $\chi^{(3)}_{IJKL}$ expresson is
\begin{equation}\label{chi3}
\begin{split}
		\chi^{(3)}_{IJKL} &= NF(\omega_4) \langle \gamma_{ijkl} \rangle \sim \langle \beta_{ijk} \mu_l \rangle\\
\end{split}
\end{equation}
The steps behind orientational averaging of $\gamma_{ijkl}$, a rank four tensor in the molecular frame, are detailed elsewhere.\cite{Andrews1977, McDonnell2024}
Orientational averaging shows specific polarization schemes isolate linear combinations of different $\beta_{ijk}$ terms. 
Infrared spectra can provide values for different $\vec{\mu}$ components.
Since $\vec{\mu}$ is a rank-one tensor, its three Cartesian components share the simple relationship $\langle {\mu^2_x} \rangle = \langle {\mu^2_y} \rangle = \langle {\mu^2_z} \rangle = \frac{1}{3}\langle {\mu^2} \rangle$. \cite{RN459}
Neglecting rotational dependence, $\langle {\mu^2} \rangle = \abs{\mu}^2 = \mu^2$.
Substituting into \autoref{chi3} shows that
\begin{subequations}
	\begin{equation}
		\begin{split}
			\langle \gamma_{ijkl} \rangle &\sim \langle \beta_{ijk} \mu_l \rangle\\
			&\sim \langle \beta_{ijk} \rangle \frac{\mu}{\sqrt{3}} 
		\end{split}
	\end{equation}
This is done because any element of $\vec{\mu}$ is easily related to its magnitude through the directional cosine relationship shown above. 
Continuing by substituting in the results found in \autoref{SIVEselection}, we see
	\begin{equation}
		\langle \beta_{ijk} \rangle = - 24\sqrt{3} \frac{\hbar \varepsilon_0 \Delta_{gv}}{NF(\omega_4)\rho_{gg}} \frac{\chi^{(3)}_{IJKL}}{\mu}
	\end{equation}
\end{subequations}
Since $\mu^2$ can be extracted by fitting infrared spectra,\cite{RN412} it is clear that different polarization schemes in SIVE spectroscopy give a measurement of $\beta_{ijk}$ values.
SIVE can therefore provide useful insight into the sensitivity of hyper-Raman spectroscopy to different infrared active vibrations.

>>>>

\graphicspath{{"figures/"}}
\begin{document}
%Title of paper
\title{Coherent Hyper-Raman Four Wave Mixing Vibrational Spectroscopies}

@@

Most quantitative methods in an n$^{th}$ order CMDS experiment are used to extract $\chi^{(n)}$ values to compare the relative strength of nonlinear processes in different media. \cite{Zhu87, RN351, RN345}
The recorded $\chi^{(n)}$ values provide insight into how microscopic quantities ($\vec{\mu}, \alpha_{ij}, \beta_{ijk}$) impact nonlinear output.
To our knowledge, only vibraitonal SFG and 2D-IR spectroscopy has taken advantage of orientationally averaged $\chi^{(n)}$ values to extract transition moments. \cite{Shen90, Moilanen2009, RN245}
Previous treatments did not consider using quantitative analysis in SIVE to measure $\beta_{ijk}$ values from SIVE spectra.
It is thus useful to investigate how a simple treatment of orientational averaging can extract $\beta_{ijk}$ from a $\chi^{(3)}_{IJKL}$ expression.

The SIVE $\chi^{(3)}_{IJKL}$ expression is
\begin{equation}\label{chi3}
\begin{split}
		\chi^{(3)}_{IJKL} &= NF(\omega_4) \langle \gamma_{ijkl} \rangle \sim \langle \beta_{ijk} \mu_l \rangle\\
\end{split}
\end{equation}
This expression cannot be exactly used to extract $\beta_{ijk}$, as $\beta_{ijk}$ is a Hermitian operator but $\Delta_{gv} \in \mathbb{C}$. 
However, when on resonance, $\Delta_{gv} = -i\Gamma_{gv}$.
Thus, below we consider cases where the experiment is resonant, so that $\chi^{(3)}_{IJKL}$ is purely imaginary, or, (insert equation).
Clearly, we can then see that $\langle \beta_{ijk} \mu_l \rangle \sim -\frac{1}{\Gamma_{gv}}\Im(\chi^{(3)}_{IJKL})$

The steps behind orientational averaging of $\gamma_{ijkl}$, a rank four tensor in the molecular frame, are detailed elsewhere.\cite{Andrews1977, McDonnell2024}
Orientational averaging shows specific polarization schemes isolate linear combinations of different $\beta_{ijk}$ terms. 
Infrared spectra can provide values for different $\vec{\mu}$ components.
Since $\vec{\mu}$ is a rank-one tensor, its three Cartesian components share the simple relationship $\langle {\mu^2_x} \rangle = \langle {\mu^2_y} \rangle = \langle {\mu^2_z} \rangle = \frac{1}{3}\langle {\mu^2} \rangle$. \cite{RN459}
Neglecting rotational dependence, $\langle {\mu^2} \rangle = \abs{\mu}^2 = \mu^2$.
Substituting into \autoref{chi3} shows that
\begin{subequations}
	\begin{equation}
		\begin{split}
			\langle \gamma_{ijkl} \rangle &\sim \langle \beta_{ijk} \mu_l \rangle\\
			&\sim \langle \beta_{ijk} \rangle \frac{\mu}{\sqrt{3}} 
		\end{split}
	\end{equation}
This is done because any element of $\vec{\mu}$ is easily related to its magnitude through the directional cosine relationship shown above. 
Continuing by substituting in the results found in \autoref{SIVEselection}, we see
	\begin{equation}
		\langle \beta_{ijk} \rangle = - 24\sqrt{3} \frac{\hbar \varepsilon_0 \Delta_{gv}}{NF(\omega_4)\rho_{gg}} \frac{\chi^{(3)}_{IJKL}}{\mu}
	\end{equation}
\end{subequations}
Since $\mu^2$ can be extracted by fitting infrared spectra,\cite{RN412} it is clear that different polarization schemes in SIVE spectroscopy give a measurement of $\beta_{ijk}$ values.
SIVE can therefore provide useful insight into the sensitivity of hyper-Raman spectroscopy to different infrared active vibrations.
